Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-29 frontiers.tex
Fix title

\title[Transmembrane helices are 
  an overlooked and evolutionarily conserved
  source of major histocompatibility complex class I and II epitopes
]{Transmembrane helices are 
  an overlooked and evolutionarily conserved
  source of major histocompatibility complex class I and II epitopes
}

>>>>

\title[Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes
]{Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes
}
